Quantum-assisted unsupervised data clustering

### 2020-05-05 manuscript.tex
Change for issue #22

\section{Discussions}
We have developed a quantum assisted SOFM and showed a proof-of-concept experimental demonstration 
that it can be used to solve clustering problems in an unsupervised manner.  
The procedure of solving such clustering problem requires calculating the distance many times in iterative way, 
which is calculated using a hybrid quantum-classical procedure.  
We introduced an optimized circuit for Hamming distance calculations that can be implemented on currently available quantum computing devices with high fidelity. 
Our quantum circuit performs the distance-computing component of a classical SOFMs algorithm 
and in this way improve its performance. 
The complexity of the quantum assisted SOFM scales as $O(LN)$ 
while the complexity of the fully classical SOFM scales as $O(LMN)$, 
where $N$ is number of samples, $M$ is number of randomly sampled cluster vectors, 
and $L$ is number of the shifts of cluster vectors.
Due to wide use of classical SOFMs in different areas of modern research and technology, 
this can give opportunities for the use of QASOFM in practical applications in near term, outperforming classical algorithms.

>>>>

\section{Discussions}
We have developed a quantum assisted SOFM and showed a proof-of-concept experimental demonstration
that it can be used to solve clustering problems in an unsupervised manner.
The procedure of solving such clustering problem requires calculating the distance many times in iterative way,
which is calculated using a hybrid quantum-classical procedure.
We introduced an optimized circuit for Hamming distance calculations that can be implemented on currently available quantum computing devices with high fidelity.
Our quantum circuit performs the distance-computing component of a classical SOFMs algorithm
and in this way improve its performance.
The complexity of the quantum assisted SOFM scales as $O(LN)$
while the complexity of the fully classical SOFM scales as $O(LMN)$,
where $N$ is number of samples, $M$ is number of randomly sampled cluster vectors,
and $L$ is number of the shifts of cluster vectors.
Due to wide use of classical SOFMs in different areas of modern research and technology,
this can give opportunities for the use of QASOFM in practical applications in near term, outperforming classical algorithms. \hl{In addition, as our algorithm performs the Hamming distance calculation, it has potential to enhance any classical algorithm that relies on calculating distances between data entries of vector form. In machine learning, data science, statistics and optimization, distance is a common way of representing similarity, calculating it between large data sets is common procedure and our circuit could potentially enhance other distance-based algorithms as long as exact distance is not required, but when knowledge of nearest vectors is sufficient.}
